Cloud Manufacturing xxx from a ecosystem view

### 2016-03-24 background.tex
描述完框架图
接下来列出要做什么，逐步完成

\begin{figure}[htbp]
\centering
\includegraphics[scale = .6, trim = 0 15 0 10]{supplementary.pdf}
\caption{Supplementay Illustration of \autoref{fig:structure}}
\label{fig:supplementary}
\end{figure}

The architecture of Cloud Manufacturing is mainly comprised by three parts, namely, \begin{inparaenum}[1)]
\item User,
\item Platform and
\item Physical Base
\end{inparaenum}, some of whose subparts are connected by material or information flows. With the supplementary illustration of \autoref{fig:supplementary}, which categorizes the main applications in Cloud Manufacturing environment with the forementioned flows that marked by circled number (i.e. \textcircled{\small{1}}), a simple version of conception for Cloud Manufacturing architecture we study here can be described as follows:

>>>>

The architecture of Cloud Manufacturing is mainly composed of three parts, namely, \begin{inparaenum}[1)]
\item User,
\item Platform and
\item Physical Base
\end{inparaenum}, that are connected by material or information flows. A simple version of conception for Cloud Manufacturing architecture we study here can be described as follows:
\begin{compactdesc}
\item [User] part describes the main roles in the Cloud Manufacturing environment like manufacturing service provider and manufacturing service demander, whome can be called as provider and demander for short respectively, from the functional point of view. Meanwhile, these roles can also be classified into enterprise user and customer, from the practical point of view. Both functional and practical are important perspective for later analysis in following sections. 
\item [Platform] part consists of 3 main layers namely \begin{inparaenum}[1)]
\item Application/Interface Layer,
\item Service Layer and 
\item Resource \& Production Layer
\end{inparaenum}.
Service is the core idea of Cloud Manufacturing, so Service Layer is the core of the Cloud Manufacturing platform. With the help of related technology in servitization, manufacturing resource and production can be encapsulated into services, then these services can be acquired by users with the well designed applications or interfaces.
\item [Physical Base] part includes the basic infrastructure, resource and production. It's worth mentioning that part of resources and production can even be virtualized with some services the platform provides.
\end{compactdesc}

\begin{figure}[htbp]
\centering
\includegraphics[scale = .6, trim = 0 15 0 10]{supplementary.pdf}
\caption{Supplementay Illustration for \autoref{fig:structure}}
\label{fig:supplementary}
\end{figure}

With the supplementary illustration of \autoref{fig:supplementary}, which categorizes the main applications in Cloud Manufacturing environment with the forementioned flows that marked by circled number (i.e. \textcircled{\small{1}}) and corresponding to the same symbol in \autoref{fig:structure}, we can simply describe the main activities within the Cloud Manufacturing system. In \autoref{fig:supplementary}, we denote provider, demander, platform and physical base as \textbf{P}, \textbf{D}, \textbf{PF} and \textbf{PB} respectively. The overlap among application districts implies the complexity of the system, so that we will analyse these applications coordinately from a system view.

### 2016-03-24 review.tex
adjust the structure
描述完框架图
接下来列出要做什么，逐步完成

Currently, the literature review indicates that modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework (Tao, Zhang, et al. 2012;Valilai and Houshmand 2013)
% subsection cloud_manufacturing (end)

@@

\subsubsection{Cellular Automata}
% subsection complex_system (end)
% section literature_review (end)

>>>>

Currently, the literature review indicates that modular approaches and multi-layer architectures are the most common way to build the cloud manufacturing platform or system framework (Tao, Zhang, et al. 2012;Valilai and Houshmand 2013)

\textbf{Services and Tasks}

Cloud Manufacturing Ecosystem provides a platform which distributed manufacturing resources/orders gathered as resources/orders hub. In order to complete orders precisely, order will be splited into tasks. Similarly, resources will be bundled into services for the quick searhing.

\textbf{Roles}

Most recent studies like Wu et al.\cite{Wu2013} described the roles in Cloud Manufacturing as a tri-group model with:\begin{inparaenum}[1)]
\item Users/Customers,
\item Application providers and
\item Physical resource providers.
\end{inparaenum}
However, the roles in real world always not go like this model, since it parted roles only by their functions. While, users could get different function roles depend on what transaction they take, we should make some modifiacations on this model.

Before the emendation of the roles, some related standard name should be taken:
\begin{asparadesc}
\item[User] The main role in Cloud Manufacturing, which is combined of Seller and Buyer as shown in \autoref{tab:categoryuser}, usually acts as Seller or Buyer according to the specific transaction;
\item[Seller] The temporary role in a transaction, which provides the allocated part of manufacturing service and makes a evalution about the Buyer after the transaction;
\item[Buyer] The temporary role in a transaction, which submits the allocated part of manufacturing task and makes a evalution about the Seller after the transaction;
\item[Administrator] The role that gets the work for the operation and maintenance of the platform, has indirectly impact on the Ecosystem.
\end{asparadesc}
\begin{table}[htbp]
  \centering\small
  \caption{Category of Users}
    \begin{tabularx}{\textwidth}{llccX}
    \toprule
        &  & Seller & Buyer & Description \\
    \midrule
    Generalized & User & $\surd$ & $\surd$ & Act as Seller or Buyer according to the specific transaction. \\
    Enterprise & User & $\surd$ & &  Provides the allocated part of manufacturing services and makes a evalution about the Buyer after the transaction. \\
    Customer & User& & $\surd$ &  Submits the allocated part of manufacturing tasks and makes a evalution about the Seller after the transaction.\\
    \bottomrule
    \end{tabularx}%
  \label{tab:categoryuser}%
\end{table}%
As defined above, Enterprise User is the special case of the User(short for Generalized User) that purely provides manufacturing services and the Customer User is similarly defined.

Hence, there is only two roles in the Ecosystem worth to be studied: User and Administrator, the proportion of user type could be adjusted as the runtime of the system goes by.

% subsection cloud_manufacturing (end)

@@

\subsubsection{Cellular Automata}

\subsubsection{Agent-based Modeling}
% subsection complex_system (end)
% section literature_review (end)
